Predicting sales of newly published books

### 2015-08-21 paper.tex
comenzando la sección Experiments and Results

Once the methods to be applied have been chosen, they must be applied to data sets 
to obtain the prediction models for each one. 
Later on, the models ability must be validated on non-previously seen data.

@@

% Mean absolute error MAE
% Root mean squared error RMSE
% Relative absolute error RAE
% Root relative squared error RRSE

  %[pedro] ya están todos los resultados de tabla:results13 para MP5, LR, KNN, SVM y MLP

  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
Obtained results using the different forecasting methods on the dataset with 13 
variables per book can be shown in Table \ref{tabla:results13}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	  & MAE 			& RMSE 		& RAE (\%)		& RRSE (\%) 		\\
\hline
  MP5 		& 2.94 $\pm$ 0.51 	& 65.49 	& 133.73 	& 11.10 	& 9.17 	  \\
\hline
  LR 		  & 0.33 $\pm$ 0.07 	& 100.813 & 257.63 	& 17.09 	& 17.67 	\\
\hline
  SVM 		& 49.10 $\pm$ 8.05	& 52.30	  & 139.45	& 8.87    & 9.56  	\\
\hline
  KNN 		& 0.03 $\pm$ 0.01 	& 198.16 	& 542.93 	& 33.59 	& 37.24 	\\
\hline
  MLP 		& 12.70 $\pm$ 3.08 	& 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

@@

>>>>

Once the methods to be applied have been chosen, they must be applied to data sets 
to obtain the prediction models for each one. 
Later on, the models ability must be validated on non-previously seen data.
Specifically, instead of using the conventional validation strategy based on 
using a training set and later on a testing set (unknown data against which 
the model must be tested), a cross-validation technique \cite{Geisser1993,Kohavi1995,Devijver1982} 
has been used to estimate how accurately the predictive model will perform in 
practice. %, limiting at the same time the overfitting problem.

@@

% Comentar que:
% - se ha usado la implementación de estos 5 métodos del paquete WEKA
% - se han realizado 30 ejecuciones con cada método
% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU @ 3.00GHz (4 cores), 16 GB RAM
% - 
% - 
% Preparar tests estadísticos para ver si hay diferencias en los errores entre métodos.
% - 
% -

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
Obtained results using the different forecasting methods on the dataset with 13 
variables per book can be shown in Table \ref{tabla:results13}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	  & MAE 			& RMSE 		& RAE (\%)		& RRSE (\%) 		\\
\hline
  MP5 		& 2.94 $\pm$ 0.51 	& 65.49 	& 133.73 	& 11.10 	& 9.17 	  \\
\hline
  LR 		  & 0.33 $\pm$ 0.07 	& 100.813 & 257.63 	& 17.09 	& 17.67 	\\
\hline
  SVM 		& 49.10 $\pm$ 8.05	& 52.30	  & 139.45	& 8.87    & 9.56  	\\
\hline
  KNN 		& 0.03 $\pm$ 0.01 	& 198.16 	& 542.93 	& 33.59 	& 37.24 	\\
\hline
  MLP 		& 12.70 $\pm$ 3.08 	& 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

@@

% - indicar qué método da mejores resultados
% - indicar qué método es tipo "caja-negra" y cuáles ofrecen modelos "explicables"
% - 
% -
